Describing the C-space of asynchronous periodic task using DIT

### 2013-07-25 dit-paper_ieee.tex
Better description of the linear problem

Such a linear problem can be solved by the simplex algorithm. However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. The naive method would be to test each constraints against the set of all the others, we present an efficient preprocessing slightly more efficient approach in Algorithm \ref{alg:prunRedun}.

\begin{algorithm}
\caption{Removing redundancy - first pass}
\label{alg:prunRedun}
	\begin{algorithmic}[1]
		\STATE $CSPACE$ : set of constraints
		\STATE $S \leftarrow \emptyset$
		\FOR{$cstr$ \textbf{in} $CSPACE$}
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE $S \leftarrow cstr$
			\ENDIF
		\ENDFOR

		\STATE $S_2 \leftarrow \emptyset$
		\FOR{$cstr$ \textbf{in} $S$}

	\end{algorithmic}
\end{algorithm}

@@

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. This gives us a first correct description of the C-SPACE which is not efficient. We then solve a linear integer problem per constraint which allow us to determine redundancy.

>>>>

Such a linear problem can be solved by the simplex algorithm. However, here the problem is not exactly the same as we have a set of constraints and we want to find all redundant constraints within. The naive method would be to directly test each constraints of the set against all the others, we present a similar method with an efficient preprocessing in Algorithm \ref{alg:prunRedun}.

\begin{algorithm}
\caption{Removing redundancy from CSPACE}
\label{alg:prunRedun}
	\begin{algorithmic}[1]
		\STATE $CSPACE$ : set of constraints
		\STATE $S \leftarrow \emptyset$
		\STATE \COMMENT{First pass - test $cstr$ against previous ones}
		\FOR{$cstr$ \textbf{in} $CSPACE$}
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE $S \leftarrow cstr$
			\ENDIF
		\ENDFOR
		\STATE \COMMENT{Second pass - test $cstr$ against every other}
		\FOR{$cstr$ \textbf{in} $S$}
			\STATE Remove $cstr$ from $S$
			\IF {$cstr$ is not redundant w.r.t. $S$}
				\STATE Put $cstr$ back into $S$
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

To summarize, we first reduced the number of constraint from every possible interval $[t_1, t_2]$ to only the interval where $t_1$ is an arrival and $t_2$ is a deadline between $[t_d, t_d + H]$ if $t_d$ exists, or between $[O_{max}, O_{max} + 2H]$ otherwise. After this correct but not efficient description of the C-SPACE, a linear integer approach removes the remaining redundancies.
